\thesisTitle

### 2019-10-16 proposal/paper.tex
added optional goals

\begin{enumerate}[label=\textbf{\arabic*.}]
	\item \textbf{Aggregation:}
		Define a class of aggregation functions that takes vertex scores as its input.
		It should fulfill the role of the uninorms and OWA functions in the existing LTA papers.
	\item \textbf{Disaggregation:}
		Describe how vertex features should be used to compute a constituent score that will be combined by the aggregation function.
	\item \textbf{Learning:}
		Combine the chosen aggregation and disaggregation methods into a joint LTA model with a suitable loss function.
		This model should be optimizable reasonably efficiently on modern hardware.
	\item \textbf{Implementation:}
		A reference implementation for the designed LTA model should be developed.
	\item \textbf{Evaluation:}
		The reference implementation should be used to evaluate the model on at least one test dataset.
		Due to the scarcity of graph regression datasets, the used test data might be randomly generated.
		Generated dataset should be obtained using a variety of representative deterministic graph scoring measures to check which kinds of local and global structural features are learnable;
		some examples of measures that might be part of a graph scoring functions are the count of $k$-cliques in a graph, the graph diameter, the presence of cycles or various properties of a graph's degree distribution.
\end{enumerate}

@@

In addition to the previous goals, the following goals should be pursued if possible:
\begin{itemize}
	\item
\end{itemize}

@@

\begin{enumerate}
	\item Introduction
	\item \dots
\end{enumerate}

>>>>

\begin{enumerate}[label=\textbf{\arabic*.}]
	\item \textbf{Aggregation:}
		Define a class of aggregation functions that takes vertex scores as its input.
		It should fulfill the role of the uninorms and OWA functions in the existing LTA papers (see \cref{sec:related-work:lta}).
	\item \textbf{Disaggregation:}
		Describe how vertex features should be used to compute a constituent score that will be combined by the aggregation function.
	\item \textbf{Learning:}
		Combine the chosen aggregation and disaggregation methods into a joint LTA model with a suitable loss function.
	\item \textbf{Implementation:}
		A reference implementation for the designed LTA model should be developed.
	\item \textbf{Evaluation:}
		The reference implementation should be used to evaluate the model on at least one test dataset.
		Due to the scarcity of graph regression datasets, the used test data might be randomly generated.
		Generated dataset should be obtained using a variety of representative deterministic graph scoring measures to check which kinds of local and global structural features are learnable;
		some examples of measures that might be part of a graph scoring functions are the count of $k$-cliques in a graph, the graph diameter, the presence of cycles or various properties of a graph's degree distribution.
		The results should be compared with the results of at least one other approach for learning graph scores, e.g.\ a ConvCNN with a fixed aggregation function instead of a learned one.
\end{enumerate}

@@

If possible, the previous goals could be extended.
For each of the previous five goal categories, optional additional ideas are listed below.
\begin{enumerate}[label=\textbf{\arabic*.}]
	\item \textbf{Aggregation:}
		Multiple classes of aggregation functions could be considered and compared.
	\item \textbf{Disaggregation:}
		As describen in \cref{sec:related-work:gc} there are multiple methods to learn vertex scores.
		Depending on the chosen overall approach, a few of those methods might be suitable to be combined with an aggregation function learner.
		Those suitable combinations could be evaluated and compared.
	\item \textbf{Learning:}
		The joint model of aggregation and disaggregation function learning can most likely be optimized using various algorithms.
		Those algorithms could be compared.
		In case their runtime performance is impractical in certain situations, approximations and simplifications of the model could be considered.
	\item \textbf{Implementation:}
		The chosen approach should ideally align well with the practical constraints of implementation.
		It should be suitable for an implementation on modern GPUs and/or distributed cluster environments.
	\item \textbf{Evaluation:}
		It would be interesting to not only use generated data but also a real dataset for evaluation (see \cref{sec:related-work:gr}).
\end{enumerate}

@@

\begin{enumerate}
	\item Introduction
	\item
	\item Evaluation
	\item Conclusion
	\item Literature
	\item Appendix
\end{enumerate}
